Rugsafe: A Multichain Vault Protocol for Defending Against Rug Pulls

### 2024-09-04 hello_world/rugsafe/paper/paper.tex
saved

\[
\text{Rug Creator's Swap} = \text{Large Supply of Rug Token} \rightarrow \text{Withdrawal of All Liquid Tokens}
\]

@@

Through mechanisms like bonding, claim processes, and community-driven challenge periods, the Rugsafe protocol provides a robust framework to protect users from potential rug pulls. By requiring issuers to post a bond at token issuance and allowing the community to challenge suspected rug pulls, the protocol empowers users to take proactive steps in safeguarding their investments.

>>>>

\[
\text{Swap} = \text{Rug Token (Large Supply)} \rightarrow \text{Liquid Token (Full Withdrawal)}
\]

@@

Through mechanisms like bonding, claim processes, and community-driven challenge periods, the Rugsafe protocol provides a protocol to protect users from rug pulls. By requiring issuers to post a bond at token issuance and allowing the community to challenge suspected rug pulls, the protocol empowers users to take proactive steps in safeguarding their investments.
